Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-11-09 analysis/paper/paper.Rmd
updated data filepaths in paper for "raw_data" change

```{r cmr-effort-data}
cmr_df = read_csv("../data/raw data/deadwater_cmr_effort_20210614.csv") %>%
  clean_names()

@@

```{r shoup-temp-data}
temp_df = read_tsv("../data/raw data/USGS_13307000_Salmon_River_Nr_Shoup.txt",
                   comment = "#") %>%
  rename(discharge_cfs = `47768_00060`,
         discharge_cfs_cd = `47768_00060_cd`,
         gage_ht_ft = `47769_00065`,
         gage_ht_ft_cd = `47769_00065_cd`,
         water_temp_c = `47773_00010`,
         water_temp_c_cd = `47773_00010_cd`)

@@

```{r map, out.width = "85%", fig.cap = "Map of the Deadwater Slough study area. The high-resolution orthoimage portion directly surrounding the Deadwater Slough was generated from aerial images taken by a drone. The red polygon indicates the reach characterized by unnaturally slow water velocities and a deepened channel. The location of the Dump Creek delta is indicated."}
knitr::include_graphics("../figures/deadwater_map.png")

>>>>

```{r cmr-effort-data}
cmr_df = read_csv("../data/raw_data/deadwater_cmr_effort_20210614.csv") %>%
  clean_names()

@@

```{r shoup-temp-data}
temp_df = read_tsv("../data/raw_data/USGS_13307000_Salmon_River_Nr_Shoup.txt",
                   comment = "#") %>%
  rename(discharge_cfs = `47768_00060`,
         discharge_cfs_cd = `47768_00060_cd`,
         gage_ht_ft = `47769_00065`,
         gage_ht_ft_cd = `47769_00065_cd`,
         water_temp_c = `47773_00010`,
         water_temp_c_cd = `47773_00010_cd`)

@@

```{r map, out.width = "85%", fig.cap = "Map of the Deadwater Slough study area. The high-resolution orthoimage portion directly surrounding the Deadwater Slough was generated from aerial images taken by a drone. The red polygon indicates the reach characterized by unnaturally slow water velocities and a deepened channel. The location of the Dump Creek delta is indicated."}
knitr::include_graphics("../figures/deadwater_map_low_res.png")
